---
title: ET_VoE_animations: Dwell time analysis
author: Christoph Voelter
date: 03/12/2020
output: html_document
---
notes: look at gap AI, 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
library(tidyverse)
library(summarytools)
library(exactRankTests)
library(ggpubr)

```

### Summary


Read Data
```{r}
orig.data <- read_csv("data/ET_VoE_occlusion_IA_report.csv")



demo.data <- read_csv("data/VoE_Occlusion_demographics and counterbalancing.csv")%>%
  mutate(EDF1=fct_recode(EDF1, Georgia_2="Georgia2", Georgia_1="Georgia1", Cheynna_1="Cheynna1"))%>%
  separate(EDF1, c("subject", "xx"), sep="_")%>%
  select(-comment)



xdata <- orig.data %>%
  select(Session_Name_, IP_LABEL, IA_LABEL,IA_ID, Trial_Index_, condition, phase, session,  video_file, video_id, video_latency, DATA_FILE,  IA_AREA, IA_AVERAGE_FIX_PUPIL_SIZE,  IA_DWELL_TIME, "IA_DWELL_TIME_%", IA_FIXATION_COUNT, IA_MAX_FIX_PUPIL_SIZE, INTEREST_AREA_FIXATION_SEQUENCE, TRIAL_DWELL_TIME, TRIAL_FIXATION_COUNT, TRIAL_IA_COUNT, TRIAL_TOTAL_VISITED_IA_COUNT )%>%
  mutate(Session_Name_=fct_recode(Session_Name_, Georgia_2="Georgia2",Georgia_1="Georgia1", Cheynna_1="Cheynna1", Cheynna_2="Cheynna2" ))%>%
  separate(Session_Name_, c("subject", "session.num"), sep="_")%>%
    mutate(session.num=fct_recode(as.factor(session.num), "2"="3" ))%>%
  full_join(demo.data)%>%
  rename(trial="Trial_Index_")
  

#checks:
view(dfSummary(xdata))


table(xdata$condition, xdata$subject)
table(xdata$session.num, xdata$subject)
table(xdata$condition, xdata$TRIAL_TOTAL_VISITED_IA_COUNT)

```



Plotting pole data:
dogs look significantly longer at pole IA in the experimental condition than in the control condition at the end of the video.

End IP
```{r}

test.IP.end.data <- xdata %>%
  filter(condition!="hab", IP_LABEL=="IP_End")


ggplot(data = test.IP.end.data, aes(x=condition, y=IA_DWELL_TIME))+
  geom_boxplot(alpha=0.5)+#, outlier.colour = "white")+
  #geom_point(aes(x=first_target_loc, y=IA_DWELL_TIME, group=IA_LABEL),position_dodge(), alpha=0.5)+
  facet_wrap(~IA_LABEL)+
  ylab("Dwell time")+xlab("Condition")+
  #ylim(0,3000)+
  theme_bw()+
  stat_compare_means(paired = TRUE, method = "t.test", label.y = 1500 )


```

```{r}
test.IP.end.IA.poledata <- xdata %>%
  filter(condition!="hab", IP_LABEL=="IP_End", IA_LABEL=="pole_AOI")


t.test(test.IP.end.IA.poledata$IA_DWELL_TIME[test.IP.end.IA.poledata$condition=="exp"], test.IP.end.IA.poledata$IA_DWELL_TIME[test.IP.end.IA.poledata$condition=="con"], paired=TRUE)
```


### Onscreen Dwell time (while videos is playing)

```{r}
on_scree_data<-read.delim("data/ET_VoE_Occlusion_IA_report_video_period.txt", header=TRUE, na=".", sep = "\t")%>%
  filter( IA_LABEL=="right_AOI")%>%
  mutate(ip_duration=IP_END_TIME-IP_START_TIME, prop_looking=TRIAL_DWELL_TIME/ip_duration)%>%
    mutate(EDF=fct_recode(Session_Name_, Georgia_2="Georgia2",Georgia_1="Georgia1", Cheynna_1="Cheynna1", Cheynna_2="Cheynna2" ))%>%
  separate(EDF, c("subject", "session.num"), sep="_")%>%
  select(Session_Name_, subject, condition, phase, TRIAL_DWELL_TIME, ip_duration, prop_looking)%>%
  mutate(condition=as.factor(condition))


on_scree_data%>%group_by(condition)%>%
  summarise(median=median(prop_looking, na.rm = TRUE),mean=mean(prop_looking, na.rm = TRUE), se=sd(prop_looking, na.rm = TRUE)/sqrt(length(prop_looking)), min=min(prop_looking, na.rm = TRUE), max=max(prop_looking, na.rm = TRUE))

```

onscreen dwell-time: comparison between first and last familiarisation trial.
```{r}
library(broom)
on_scree_data%>%filter(phase=="hab1" | phase=="hab3")%>%
  group_by(subject, phase)%>%
  summarise(mean=mean(prop_looking, na.rm=TRUE))%>%
  ungroup()%>%
  summarise(ttest = list(t.test(mean ~ phase, paired=TRUE)))%>%
  mutate(ttest = map(ttest, tidy)) %>%
  unnest()
```


onscreen dwell-time: comparison between test trials
```{r}
on_scree_data%>%filter(phase=="test")%>%
  group_by(subject, condition)%>%
  summarise(mean=mean(prop_looking, na.rm=TRUE))%>%
  ungroup()%>%
  summarise(ttest = list(t.test(mean ~ condition, paired=TRUE)))%>%
  mutate(ttest = map(ttest, tidy)) %>%
  unnest()
```

Plot onscreen dwell time in test trials
```{r}
xx<-on_scree_data%>%filter(phase=="test")%>%
  group_by(subject, condition)%>%
  summarise(mean=mean(prop_looking, na.rm=TRUE))%>%
  ungroup()

ggplot(data=xx, aes(x=condition, y=mean))+
  geom_boxplot()
```