---
title: "Power simulation: From VoE to exploation"
author: "Christoph Völter"
date: "09/01/2022"
output: 
  html_document:
    theme: united
    toc: yes
    toc_depth: 4
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
library(tidyverse)
library(cowplot)
library("gghalves")
library(ggthemes)

#load(".RData")

```

## Generate data

```{r echo=FALSE, include=FALSE}

set.seed(1)
n.subject <- 68# number subjects
n.per.subject <- 1 # observations per subject
n.per.condition <- 1 # observations per subject and condition
subj.id <- as.factor(paste("subj", 1:n.subject, sep = "."))
age.range=c(1:13)

inc.per <- c(0.65, 0.67) # performance in incongruent condition
con.per <- c(0.3, 0.33) # performance in congruent condition

start.data <- data.frame(subj.id)
xdata=data.frame(expand.grid(condition=c("con", "inc"), sex=c("F", "M")))

start.data<-cbind(start.data, xdata)
```


## Simulation

```{r eval=FALSE, include=FALSE}
n.simus <- 1000 # small number for testing


# create object to store the simulation parameters and results:
all.res <- data.frame(expand.grid(
  n.per.subject = n.per.subject, 
  inc.per = inc.per,
  con.per = con.per,
  simu = 1:n.simus
))
all.res$icpt <- NA
all.res$conditioninc <- NA
all.res$z.age <- NA
all.res$sexM <- NA
all.res$warns.full <- NA
all.res$warns.null <- NA
all.res$lrt.p.con <- NA
all.res$lrt.p.age <- NA
all.res$full.null.p <- NA

all.ests <- matrix(NA, nrow = n.simus, ncol = 1)
colnames(all.ests) <- c("lrt.p.con")

# create data frame with design:
## done above

# load packages needed:
library(lme4)
# Loading required package: Matrix
library(kyotil) # we want to store info about convergence issues

# define control structure to make convergence more likely:
xdata <- start.data

# run simulation
for (i in 1:nrow(all.res)) {
  set.seed(i) # allows to later replicate individual simulations

  # add age  (if it should be generated in each loop)
  age <- sample(x = age.range, size = length(unique(xdata$subj.id)), replace = T)
  xdata$age <- as.numeric(age[as.numeric(xdata$subj.id)])
  xdata$z.age <- as.vector(scale(xdata$age))

  m.mat <- model.matrix(object = ~ condition+sex+z.age, data = xdata) # create model martix

  coefs <- c(
    "(Intercept)" = qlogis(all.res[i, "con.per"]),#performance in congruent condition
    "conditioninc" = qlogis(all.res[i, "inc.per"])-qlogis(all.res[i, "con.per"]),#performance in incongruent condition
    "sexM" = 0,
    "z.age" = 0
  )

  LP <- m.mat[, names(coefs)] %*% coefs # LP wrt fixed effects

  # generate response:
xdata$choice <- rbinom(n = nrow(xdata), size = 1, prob = exp(LP) / (1 + exp(LP)))

  # fit full model:
  full <- keepWarnings(glm(choice~condition+sex+z.age,
			 family=binomial, data=xdata
    ))
  # fit null model:
  null <- keepWarnings(glm(choice ~ sex+z.age,
			 family=binomial, data=xdata
  ))
  # store results:
  all.res[i, c("icpt", "conditioninc", "z.age", "sexM")] <- coef(full$value)
  all.res[i, "warns.full"] <- nchar(paste(full$warnings, collapse = ""))
  all.res[i, "warns.null"] <- nchar(paste(null$warnings, collapse = ""))
  all.res[i, "lrt.p.con"] <- as.data.frame(drop1(full$value, test = "Chisq"))["condition", "Pr(>Chi)"]
  all.res[i, "lrt.age.p"] <- as.data.frame(drop1(full$value, test = "Chisq"))["z.age", "Pr(>Chi)"]
    all.res[i, "full.null.p"] <- as.data.frame(anova(null$value, full$value, test = "Chisq"))[2, "Pr(>Chi)"]
}

save.image("voe_exploration_simulation_N70.RData")
```

## Evaluation of results 

## Only models that converged are evaluated from here on:  

```{r include=FALSE}
all.res2=subset(all.res, warns.full==0)
```


### How many models converged, have a significant full-null model comparison, and a significant LRT of condition?  
```{r echo=FALSE}
n.converged<- all.res2%>%
      summarise(n.converged=length(lrt.p.con))


lrt.data2 <- all.res2 %>%
  filter(full.null.p<0.05)%>%
  group_by(inc.per,con.per) %>%
  summarise(lrt.p.con.median = median(lrt.p.con), 
            lrt.p.age.median = median(lrt.age.p),
            n.sign.lrt.con = length(lrt.p.con[lrt.p.con < 0.05]),
            n.sign.lrt.age = length(lrt.age.p[lrt.age.p < 0.05]),
            n.lrt = n.simus,
            proportion.sign.lrt.con = length(lrt.p.con[lrt.p.con < 0.05]) / n.simus,
            proportion.sign.lrt.age = length(lrt.age.p[lrt.age.p < 0.05]) / n.simus)

lrt.data2
```
#### Plotting the proportion of significant LRTs for the predictor variable condition ONLY based on models that converged and with a significant full-null model comparison

```{r echo=FALSE}
p.con.power <- ggplot(data = lrt.data2, aes(x= as.factor(inc.per),y = proportion.sign.lrt.con, fill=as.factor(con.per))) +
  geom_bar(stat="identity", color="black", position=position_dodge())+
  scale_y_continuous(breaks=seq(0,1,0.2), limits=c(0, 1))+
  geom_hline(yintercept = 0.8, colour = "black", lwd = 1.1, lty = 2) +
    geom_hline(yintercept = 0.05, colour = "darkgrey", lwd = 1.1, lty = 4) +
  scale_fill_manual(values=c("dodgerblue", "darkorange"))+
  labs(fill = "congruent condition", y="Power", x= "incongruent condition") +
  theme_few()#+
  #theme(legend.position="none")
p.con.power

ggsave(p.con.power, filename = "./graphics/voe_exploration_choice_simulation_binomial_glm.png", scale = 0.8, height = 5, width = 7)
```