---
title: "Power simulation: From VoE to exploation"
author: "Christoph Völter"
date: "09/01/2022"
output: 
  html_document:
    theme: united
    toc: yes
    toc_depth: 4
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
library(tidyverse)
library(cowplot)
library("gghalves")
library(ggthemes)

#load(".RData")

```

## Generate data

```{r echo=FALSE, include=FALSE}
set.seed(23)
n.subject <- 68# number subjects
n<-68 #sample size
n.per.subject <- 1 # observations per subject
n.per.condition <- 1 # observations per subject and condition
subj.id <- as.factor(paste("subj", 1:n.subject, sep = "."))
age.range=c(1:13)

start.data <- data.frame(subj.id)
xdata=data.frame(expand.grid(condition=c("con", "inc"), sex=c("F", "M")))

start.data<-cbind(start.data, xdata)
m.mat=model.matrix(object=~condition+sex, data=start.data)
```


```{r echo=FALSE, include=FALSE}
coefs=rep(x=0, times=ncol(m.mat))#begin with vector filled with 0s
names(coefs)=colnames(m.mat)#name it
coefs["(Intercept)"]=5#set intercept to 3
coefs["conditioninc"]=4#and effect of incongruent condition to 3
resid.sd=5#give residual standard deviation a value
rv=m.mat[, names(coefs)]%*%coefs+rnorm(n=n, sd=resid.sd)
rv[rv < 0] <- 0   
par(mar=c(2.7, 2.7, 0.2, 0.2), mgp=c(1.5, 0.3, 0),
tcl=-0.15, las=1, cex.lab=0.7, cex.axis=0.5)

plot(start.data$condition, rv)

```

## Simulation

```{r}
n.simus=10000#number simulations
res.con=rep(x=NA, time=n.simus)
res.sex=rep(x=NA, time=n.simus)
res.age=rep(x=NA, time=n.simus)

set.seed(1)
xdata<-start.data

for(i in 1:n.simus){
#sample number participants:
#n.part=sample(x=range.n.part, size=n.courses, replace=T)
  
age <- sample(x = age.range, size = length(unique(xdata$subj.id)), replace = T)
xdata$age <- as.numeric(age[as.numeric(xdata$subj.id)])
xdata$z.age <- as.vector(scale(xdata$age))
  
#generate response:
resp=m.mat[, names(coefs)]%*%coefs+rnorm(n=n, sd=resid.sd)
resp[resp < 0] <- 0   
#fit model:
model.res=summary(lm(resp~condition+sex+z.age, data=xdata))$coefficients
#determine and store result:
res.con[i]=model.res["conditioninc", "Pr(>|t|)"]<=0.05
res.sex[i]=model.res["sexM", "Pr(>|t|)"]<=0.05
res.age[i]=model.res["z.age", "Pr(>|t|)"]<=0.05
}

mean(res.con)
mean(res.sex)
mean(res.age)
```


## Evaluation of results 

## Only models that converged are evaluated from here on:  

```{r include=FALSE}
all.res2=subset(all.res, warns.full==0)
```


### How many models converged, have a significant full-null model comparison, and a significant LRT of condition?  
```{r echo=FALSE}
n.converged<- all.res2%>%
      summarise(n.converged=length(lrt.p.con))


lrt.data2 <- all.res2 %>%
  filter(full.null.p<0.05)%>%
  group_by(inc.per,con.per) %>%
  summarise(lrt.p.con.median = median(lrt.p.con), 
            lrt.p.age.median = median(lrt.age.p),
            n.sign.lrt.con = length(lrt.p.con[lrt.p.con < 0.05]),
            n.sign.lrt.age = length(lrt.age.p[lrt.age.p < 0.05]),
            n.lrt = n.simus,
            proportion.sign.lrt.con = length(lrt.p.con[lrt.p.con < 0.05]) / n.simus,
            proportion.sign.lrt.age = length(lrt.age.p[lrt.age.p < 0.05]) / n.simus)

lrt.data2
```
#### Plotting the proportion of significant LRTs for the predictor variable condition ONLY based on models that converged and with a significant full-null model comparison

```{r echo=FALSE}
p.con.power <- ggplot(data = lrt.data2, aes(x= as.factor(inc.per),y = proportion.sign.lrt.con, fill=as.factor(con.per))) +
  geom_bar(stat="identity", color="black", position=position_dodge())+
  scale_y_continuous(breaks=seq(0,1,0.2), limits=c(0, 1))+
  geom_hline(yintercept = 0.8, colour = "black", lwd = 1.1, lty = 2) +
    geom_hline(yintercept = 0.05, colour = "darkgrey", lwd = 1.1, lty = 4) +
  scale_fill_manual(values=c("dodgerblue", "darkorange"))+
  labs(fill = "congruent condition", y="Power", x= "incongruent condition") +
  theme_few()#+
  #theme(legend.position="none")
p.con.power

ggsave(p.con.power, filename = "./graphics/voe_exploration_choice_simulation_binomial_glm.png", scale = 0.8, height = 5, width = 7)
```